Discrete Ordinates

### 2017-06-13 docprep/norris_phd_dissertation.tex
Updated thesis text
Added some TODO

\begin{ThesisAbstract}
This is the text for the abstract. Here, I explain what I did and how cool I am for doing it. Because I am awesome.

Computed tomography (CT) has become pervasive in medical diagnostics as improved imaging techniques and processing algorithms provide higher quality information to doctors. However, the exponentially increasing usage of CT has raised concerns regarding long term low-dose radiological risks. Currently, the dose to patients is computed using Monte Carlo methods and experimental tests. In other areas of radiation transport, deterministic codes have been shown to be much faster than Monte Carlo codes.

@@

The DOCTORS code was benchmarked against MCNP6 and found to have very good agreement using both a water phantom and a realistic patient phantom. DOCTORS was also found to be much faster than MCNP6, even more so with GPU acceleration.

GPU

@@

\begin{ThesisAcknowledgment}
I would like to thank my adviser, Dr. Liu and all of the other graduate students for their continued support through my graduate career. I also appreciate the time spent by my committee members helping me identify problems and provide insight to solutions.

>>>>

\begin{ThesisAbstract}
Computed tomography (CT) has become pervasive in medical diagnostics as improved imaging techniques and processing algorithms provide higher quality information to doctors. However, the exponentially increasing usage of CT has raised concerns regarding long term low-dose radiological risks. Currently, the dose to patients is computed using Monte Carlo methods and experimental tests. In other areas of radiation transport, deterministic codes have been shown to be much faster than Monte Carlo codes.

@@

The DOCTORS code was benchmarked against MCNP6 and found to have good qualitative agreement using both a water phantom and a realistic patient phantom. DOCTORS was also found to be much faster than MCNP6; MCNP takes hours to compute flux profiles that take less than a minute using DOCTORS.

A GPU algorithm was implemented that speeds up the DOCTORS code by a factor of 39.

@@

\begin{ThesisAcknowledgment}
I would like to thank my adviser, Dr. Liu and all of the other graduate students for their continued support through my graduate career. I also appreciate the time spent by my committee members helping me identify problems and provide insight to solutions. I would also like to thank my committee members for their guidance throughout my PhD work.
